Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-07 Ben_Manuscripts/transport/Draft.tex
Update tex.

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  for selective separations. In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  find that the transport of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe
  that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

%  We then present our efforts to understand how water partitions within the pores.  
  We then use the transport rates of water in and out of the pores in order to
  to justify our study of solute transport restricted to the pore region. From a 
  macroscopic perspective, it might make sense to hypothesize that water spends its time 
  exclusively in the tube-like hydrophilic pore region. Our previous work showed
  that there is a gradual compositional transition from the hydrophilic to the
  hydrophobic region which means that solutes may not necessarily stay confined
  to the centers of the pores or even within the pore region. We show that, in 
  our most viable system, water moves fastest within the pores suggesting that 
  the pores should be the focus of our mechanistic studies.

@@

  In the remainder of the paper, we describe and quantify three trapping 
  mechanisms which give rise to subdiffusive solute transport behavior. 
  We investigated the differences in solute motion, specifically their mean
  squared displacement (MSD), in conjunction with each solute's size and 
  chemical functionality. We show how distinct interactions with various
  monomer components as well as membrane water content hinders the motion 
  of solutes. We discuss how the interactions between specific solutes and
  the membrane depend on the solute's chemical functionality.
%    We present the interactions between solutes, the membrane,
%  and water in order to determine which mechanism or mechanisms dominate.
%  present our observations and explanations 
%  of the observed transport mechanisms exhibited by water and solutes. 
  %MRS2: The thesis of this paragraph could be stronger. expand ``pores will restrict motion of the solutes'' a little using the physical details about the pores; paint the picture that will be filled in with detail   
  %BJC3: redone above.
%  Given that the pores will restrict motion of the solutes, we
%  anticipate that transport will be hindered in some way.

@@

  We parameterized the interaction potential for the monomer and solutes using 
  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
  We use GAFF as it has been used extensively for use with organic molecules.
  We assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
  with QUACPAC from Openeye Scientific Software.

@@

  We observed that some water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
  Information). We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region. We 
  justify this decision with better context in Section~\ref{section:transport_water_sodium}.
  %MRS2: seems like here is where we need to provide the justification for this decision, since the decision is described here (or, explain how we will justify it later)
  %BJC3: added reference to later section.

@@

  Because the MSD of water in the pores of the 10 wt\% system is significantly
  higher than that in the tails, we restrict our studies of transport in this paper to 
  solutes in or near the pore center. Transport of solutes in the pores will be the 
  limiting factor that determines permeability and rejection. Although tail transport of water in the 
  the 5 wt\% water system is faster than pore transport, water transport overall is significantly slower
  than in the 10 wt\% system. For practical applications, a membrane with water 
  transport properties comparable to the 10 wt\% system is far more feasible than
  the 5 wt\% system.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt\% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt\% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt\% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt\% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
  smaller than those of the solutes in the 10 wt\% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_nondonors_10wt.pdf}
  \caption{}\label{fig:nondonors_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  %BJC: trying out pore region cut-off here instead of head groups.
  \includegraphics[width=\textwidth]{nondonors_rdf.pdf}
  \caption{}\label{fig:nondonors_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{nondonor_hbonds.pdf}
  \caption{}\label{fig:nondonors_hbonds}
  \end{subfigure}
  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it. 
  \caption{(a) The MSDs of solutes that can only receive hydrogen bonds are
  significantly lower than expected. (b) The solutes' radial density
  is surprisingly high in the pore region, but is balanced by an appreciable
  amount of solute trapped in the tails. (c) The low MSDs exhibited by each of these
  solutes is due to a combination of entrapment within the tail region and a high 
  degree of coordination with sodium ions.}\label{fig:nondonors}
  \end{figure}

@@

  We have examined the transport characteristics of a series of small polar
  molecules in our model of the H\textsubscript{II} phase formed by the liquid 
  crystal monomer Na-GA3C11. We found that transport of solutes is primarily
  governed by water content as well as the chemical functionality of the solute
  with respect to the chemical structure and functionality of the LLC monomer 
  and ion present.

  We learned that the MSD of solutes, water and counter ions are highly 
  dependent on LLC membrane water content. As more water is added to the system, 
  the pores become less crowded with monomer components. The MSDs of water and
  sodium ions are nearly 2 orders of magnitude larger in the 10 wt\% system 
  than in the 5 wt\% system. The amount of water in the pores deserves special
  attention when screening new monomers.

@@

  The chemical functionality of solutes influences the degree to which
  they are affected by each trapping mechanism. Simple alcohols tend to
  partition into the tail region as their hydrophobic tail increases in length.
  Alcohols and sugars with multiple hydroxyl groups are very stable
  in the pore region, but frequent hydrogen bonds with monomer head 
  groups prevent them from diffusing quickly. This effect is reduced when
  hydroxyl groups are replaced with thiol groups, but the solutes become less
  stable in the pore. Finally, solutes with carbonyl groups, which includes
  the ketones, amides and solutes that can only accept hydrogen bonds, associate
  with sodium ions, temporarily slowing or immobilizing them.

  %MRS2: trying something else to emphasize what we are trying to do.  Can you add a bit more detail so it's not just slowing up or speeding solutes, but slowing or speeding up solutes of a particular type?  We can emphasize chemical selectivity . . . 
  %mitigate or enhance their effect on   solute MSDs.   
  %BJC3: gave it a try. Broke into paragraphs
  Based on these trapping mechanisms, we may be able to suggest modifications
  that can be made to monomers that will modulate their effect on specific 
  solute MSDs in order to make transport even more selective for particular 
  solutes.

  Since solutes move slowly while entangled among the monomer tails,
  and since more than half of the solutes studied spend at least 40\% of their
  time in the tails, one can try to design monomers that better control the 
  partition of solutes between the pore and tail region. Solutes move into 
  the tails due both to their size and hydrophilic character. One may be 
  able to contain solutes, even small ones like methanol, by increasing
  the density of monomers close to the head groups through incorporation of 
  cross-linkable groups in the vicinity. Alternatively, removal of the ether
  linkages between the head groups and the monomer tails may decrease the 
  stability of any of the molecules we studied near the head groups and 
  force them to spend more time within the pore.

@@

  One can instead focus on designing head groups with varying hydrogen bonding
  capabilities. Increasing the number of hydrogen bonding sites on the head 
  groups may enhance the membrane's ability to trap solutes like sugars that 
  have many hydroxyl groups. Conversely, one can decrease the number of hydrogen
  bond sites, or replace them with weaker hydrogen bonding atoms like nitrogen, to
  trap less. In contrast to the system studied here, one can design the head 
  groups so they can donate hydrogen bonds, which can enhance entrapment of 
  solutes like acetone that can only accept hydrogen bonds.

@@

% LocalWords:  lyotropic LLC solutes solute permeability micropollutants RO NF
% LocalWords:  groundwaters flowback nanofiltration bruggen Nanostructured feng
% LocalWords:  nanostructured mesophases Donnan Zhou al Dischinger BJC Hmm Na
% LocalWords:  selectivities physicochemical nanopores GA pKa's protonated pKa
% LocalWords:  gallic perrin pka NaGA MeOH URE EtOH acetamide AcN propanol PrOH
% LocalWords:  butanol BtOH mercaptoethanol EG sulfoxide DMSO PG dimercapto DMP
% LocalWords:  GLY tetrahydrofuran THF tetrose dimethylformamide DMF AcOH diols
% LocalWords:  triols MSD solute's readthedocs repo GROMACS gromacs der hess wt
% LocalWords:  Antechamber bccsym molcharge QUACPAC zhou Resel equil ca gmx COM
% LocalWords:  solvate solvated Parrinello barostat subdiffusive superdiffusive
% LocalWords:  subdiffusion CTRW MSDs ageing microfriction Gierer einstein Chan
% LocalWords:  MSD's comps li Rg appoximation polson bT fr CI Luzar Chandler py
% LocalWords:  hbonds VMD Roux genion disassociated Clauset martiniano Voloshin
% LocalWords:  timescales binned RDFs RDF tortuosity carboxylate pdf sodium's
% LocalWords:  mobilities timescale diffusivity msd tailvpore methanol's tamsds
% LocalWords:  msds sublinear ztraces COMs alkane COOH HOH hbond immobilization
% LocalWords:  counterions sulfinyl substituents electronegative COH coord na
% LocalWords:  Carvajal Wu Shinoda carboxy ATPase rdf counterintuitively Amides
% LocalWords:  unhindered propanol's butanol's hydrophilicity glycol's Ketones
% LocalWords:  hybridization amides electronegativity NH ketones Thiols SOH ACI
% LocalWords:  dimercaptoethanol dimethylsulfoxide rdfs mercaptoethanol's thiol
% LocalWords:  formamide nondonors nanoporous XSEDE PSC RMACC

>>>>

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  %MRS3:
  candidates
  for selective separation membranes. 
  %MRS3: I do worry that the above makes it look like we are not acknowledging the formulation problems.  Maybe something like: 
  %''models of how chemically selective separation membranes could can function''?  So the focus is more on the science that these membranes could reveal, rather than saying they are good membranes now?  Then we talk about new membranes at the end of the introduction. Thoughts? I didn't go ahead and make  the change since it needs a bit more thought.  I'm open to other ways to reformulate.  Some of this thinking will percolate into the rest of the introduction as well.
  In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  find that the transport of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe
  that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

%  We then present our efforts to understand how water partitions within the pores.  
  We then use the transport rates of water in and out of the pores in order to
  to justify our study of solute transport restricted to the pore region. From a 
  macroscopic perspective, it might make sense to hypothesize that water spends its time 
  exclusively in the tube-like hydrophilic pore region. Our previous work showed
  that there is a gradual compositional transition from the hydrophilic to the
  hydrophobic region which means that solutes may not necessarily stay confined
  to the centers of the pores or even within the pore region. We show that, in 
  our most viable system, water moves fastest within the pores suggesting that 
  the 
  %MR3: added to be more specific - we do look at it getting into the head groups a little.
  area in and around the central
  pores should be the focus of our mechanistic studies.

@@

  In the remainder of the paper, we describe and quantify three trapping 
  mechanisms which give rise to subdiffusive solute transport behavior. 
  We describe the differences in solute motion, specifically their mean
  squared displacement (MSD), in conjunction with each solute's size and 
  chemical functionality. We show how distinct interactions with various
  monomer components as well as membrane water content hinders the motion 
  of solutes. We discuss how the interactions between specific solutes and
  the membrane depend on the solute's chemical functionality.

@@

  We parameterized the interaction potential for the monomer and solutes using 
  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
  We use GAFF as it has been used extensively for use with organic molecules.
  We assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
  with QUACPAC from OpenEye Scientific Software.

@@

  We observed that some water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
  Information). We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region. We 
  justify this decision with better context in Section~\ref{section:transport_water_sodium}.
  %MRS2: seems like here is where we need to provide the justification for this decision, since the decision is described here (or, explain how we will justify it later)
  %BJC3: added reference to later section. 
  %MRS3: We probably need to mention the amount of water there is; 40% is in the tail.  We should probably discuss density; that because of the larger tail volume, the density is about 1/X in the distal region than in the pore.

@@

  Because the MSD of water in the pores of the 10 wt\% system is significantly
  higher than that in the tails, we restrict our studies of transport in this paper to 
  solutes in or near the pore center. Transport of solutes in the pores 
  %MRS3:
  %will 
  is likely to be
  be the 
  limiting factor that determines permeability and rejection. Although tail transport of water in the 
  the 5 wt\% water system is faster than pore transport, water transport overall is significantly slower
  than in the 10 wt\% system. For practical applications, a membrane with water 
  transport properties comparable to the 10 wt\% system is far more feasible than
  the 5 wt\% system.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt\% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt\% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt\% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt\% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it.

  \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
  smaller than those of the solutes in the 10 wt\% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_nondonors_10wt.pdf}
  \caption{}\label{fig:nondonors_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  %BJC: trying out pore region cut-off here instead of head groups.
  \includegraphics[width=\textwidth]{nondonors_rdf.pdf}
  \caption{}\label{fig:nondonors_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{nondonor_hbonds.pdf}
  \caption{}\label{fig:nondonors_hbonds}
  \end{subfigure}
  \caption{(a) The MSDs of solutes that can only receive hydrogen bonds are
  significantly lower than expected. (b) The solutes' radial density
  is surprisingly high in the pore region, but is balanced by an appreciable
  amount of solute trapped in the tails. (c) The low MSDs exhibited by each of these
  solutes is due to a combination of entrapment within the tail region and a high 
  degree of coordination with sodium ions.}\label{fig:nondonors}
  \end{figure}

@@

  We have examined the transport characteristics of a series of small polar
  molecules in our model of the H\textsubscript{II} phase formed by the liquid 
  crystal monomer Na-GA3C11. We found that transport of solutes is 
  %MRS3: tweak
  %primarily
  governed by both water content as well as the interplay between the chemical functionality of the solute
  and the chemical functionality of the LLC monomer and ion making up the pore. 
  We 
  %MRS3:
  have shown
  that the MSD of solutes, water and counter ions are highly 
  dependent on LLC membrane water content. As more water is added to the system, 
  the pores become 
  %less crowded with monomer components. 
  more dilute in the monomer components.
  The MSDs of water and
  sodium ions are nearly 2 orders of magnitude larger in the 10 wt\% system 
  than in the 5 wt\% system. The amount of water in the pores 
  %MRS3:
  thus
  deserves special
  attention when screening new monomers.

@@

  The chemical functionality of solutes influences the degree to which
  they are affected by each trapping mechanism. Simple alcohols tend to
  partition into the tail region as their hydrophobic tail increases in length.
  Alcohols and sugars with multiple hydroxyl groups are very stable
  in the pore region, but 
  %frequent 
  multiple
  hydrogen bonds with monomer head 
  groups prevent them from diffusing quickly. This effect is reduced when
  hydroxyl groups are replaced with thiol groups, but the solutes become less
  stable in the pore. Finally, solutes with carbonyl groups, which includes
  the ketones, amides and solutes that can only accept hydrogen bonds, associate
  with sodium ions, temporarily slowing or immobilizing them.

  %MRS2: trying something else to emphasize what we are trying to do.  Can you add a bit more detail so it's not just slowing up or speeding solutes, but slowing or speeding up solutes of a particular type?  We can emphasize chemical selectivity . . . 
  %mitigate or enhance their effect on   solute MSDs.   
  %BJC3: gave it a try. Broke into paragraphs
  Based on these trapping mechanisms, we may be able to suggest modifications
  that can be made to monomers that will modulate their effect on specific 
  solute MSDs in order to make transport even more selective for particular 
  solutes. 
  %MRS3: I'd actually suggest connecting these; since above is a thesis statement for the next bit. 
  Since solutes move slowly while entangled among the monomer tails,
  and since more than half of the solutes studied spend at least 40\% of their
  time in the tails, one can try to design monomers that better control the 
  partition of solutes between the pore and tail region. Solutes move into 
  the tails due both to their size and hydrophilic character. One may be 
  able to contain solutes, even small ones like methanol, by increasing
  the density of monomers close to the head groups through incorporation of 
  cross-linkable groups in the vicinity. Alternatively, removal of the ether
  linkages between the head groups and the monomer tails may decrease the 
  stability of any of the molecules we studied near the head groups and 
  force them to spend more time within the pore.

@@

  One could instead focus on designing head groups with varying hydrogen bonding
  capabilities. Increasing the number of hydrogen bonding sites on the head 
  groups may enhance the membrane's ability to trap solutes like sugars that 
  have multiple hydroxyl groups. Conversely, one can decrease the number of hydrogen
  bonding sites, or replace them with weaker hydrogen bonding atoms like nitrogen, to
  trap less. In contrast to the system studied here, one can design the head 
  groups so they can donate hydrogen bonds, which can enhance entrapment of 
  solutes like acetone that can only accept hydrogen bonds.

@@

% LocalWords:  lyotropic LLC solutes solute permeability micropollutants RO NF
% LocalWords:  groundwaters flowback nanofiltration bruggen Nanostructured feng
% LocalWords:  nanostructured mesophases Donnan Zhou al Dischinger BJC Hmm Na
% LocalWords:  selectivities physicochemical nanopores GA pKa's protonated pKa
% LocalWords:  gallic perrin pka NaGA MeOH URE EtOH acetamide AcN propanol PrOH
% LocalWords:  butanol BtOH mercaptoethanol EG sulfoxide DMSO PG dimercapto DMP
% LocalWords:  GLY tetrahydrofuran THF tetrose dimethylformamide DMF AcOH diols
% LocalWords:  triols MSD solute's readthedocs repo GROMACS gromacs der hess wt
% LocalWords:  Antechamber bccsym molcharge QUACPAC zhou Resel equil ca gmx COM
% LocalWords:  solvate solvated Parrinello barostat subdiffusive superdiffusive
% LocalWords:  subdiffusion CTRW MSDs ageing microfriction Gierer einstein Chan
% LocalWords:  MSD's comps li Rg appoximation polson bT fr CI Luzar Chandler py
% LocalWords:  hbonds VMD Roux genion disassociated Clauset martiniano Voloshin
% LocalWords:  timescales binned RDFs RDF tortuosity carboxylate pdf sodium's
% LocalWords:  mobilities timescale diffusivity msd tailvpore methanol's tamsds
% LocalWords:  msds sublinear ztraces COMs alkane COOH HOH hbond immobilization
% LocalWords:  counterions sulfinyl substituents electronegative COH coord na
% LocalWords:  Carvajal Wu Shinoda carboxy ATPase rdf counterintuitively Amides
% LocalWords:  unhindered propanol's butanol's hydrophilicity glycol's Ketones
% LocalWords:  hybridization amides electronegativity NH ketones Thiols SOH ACI
% LocalWords:  dimercaptoethanol dimethylsulfoxide rdfs mercaptoethanol's thiol
% LocalWords:  formamide nondonors nanoporous XSEDE PSC RMACC TET ribose EAC
% LocalWords:  berendsen spoel Rahman bulleted Wirtz TBD equilibrations thiols
% LocalWords:  hbonding DMS linkable permeabilities Calderon Morrin TOC
